SDSS-GAIA Calibration Note

### 2022-08-12 ms.tex
adding pltos

>>>>

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_dr8star.png}
\caption{DR8 Star vs. GAIA g-mag: Color vs. $\Delta$M.  Testing GAIA mag color vs. SDSS mag - GAIA g-bmag.   GAIA g-mag is the whole filter system. SDSS-i band could be a good representative of GAIA-g.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_bp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_bp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_bp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_bp_dr8star.png}
\caption{DR8 Star vs. GAIA bp-mag : Color vs. $\Delta$M.  Note SDSS-g and SDSS-r are close to GAIA-bp}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_rp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_rp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_rp_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_rp_dr8star.png}
\caption{DR8 Star vs. GAIA rp-mag : Color vs. $\Delta$M.  Note SDSS-i and SDSS-z are close to GAIA-rp as we expected.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_dr8quasar.png}
\caption{DR8 Quasar: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_bp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_bp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_bp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_bp_dr8quasar.png}
\caption{DR8 Quasar vs. GAIA-bp mag: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_g_rp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_r_rp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_i_rp_dr8quasar.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220812_color_dmag_z_rp_dr8quasar.png}
\caption{DR8 Quasar vs. GAIA-rp mag: Color vs. $\Delta$M.  The same plot but with Quasars.  The color range of quasars are limited.}
\end{center}
\end{figure*}
